Clustering time series based on probability distributions across temporal granularities

### 2021-11-16 main.Rmd
updated range of parameterss table

```{r range-parameter}
Scenario = c("S1", "S2","S3")
designs = c(5, 4, 4)
niter = list (c(25, 20, 500), c(25, 20, 500), c(25, 20, 500))
mu = list (c(1, 2, 5), c(1, 2, 5), c(1, 2, 5))
nT = list (c(300, 1000, 5000), c(300, 1000, 5000), c(300, 1000, 5000))

df = tibble::tibble(Scenario, designs, niter, mu, nT) %>%  
  set_names("Scenario", 
            " \\# designs", 
            "niter", 
            "$\\mu$", 
            "nT") %>%
  knitr::kable(format = "latex",
             escape = FALSE,  booktabs = TRUE,
             caption = "The range of parameters used for the validation study, for the three different scenarios, number of simulations ($niter$) for each design, differences between means ($\\mu$) across granularities and series lengths ($nT$).")%>%
  kableExtra::collapse_rows(columns = 3:5)

>>>>

```{r range-parameter}
scenario = c("S1", "S2","S3")
designs = c(5, 4, 4)
niter = list (c(25, 20, 500), c(25, 20, 500), c(25, 20, 500))
mu = list (c(1, 2, 5), c(1, 2, 5), c(1, 2, 5))
nT = list (c(300, 1000, 5000), c(300, 1000, 5000), c(300, 1000, 5000))

df = tibble::tibble(scenario, " \\# designs" = designs, niter,  "$\\mu$" = mu, nT) %>%
  knitr::kable(format = "latex",
             escape = FALSE,
             caption = "The range of parameters used for the validation study, for the three different scenarios, number of simulations ($niter$) for each design, differences between means ($\\mu$) across granularities and series lengths ($nT$).")%>%
  kableExtra::collapse_rows(columns = 3:5)
